%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This is a modified ONE COLUMN version of
% the following template:
%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \documentclass[]{deedy-resume-openfont}

    \begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Profile
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Carlton}{Northern}{carlton.northern@gmail.com | (757) 967-7577 | San Diego, CA | github.com/carltonnorthern}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Skills
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Skills}
\raggedright
\begin{tabular}{ l l }
	\descript{Programming Languages} & {\location{Java, C++, Python, shell, Terraform, Puppet, JavaScript, HTML, CSS, PHP}} \\
	\descript{Platforms}             & {\location{Android, iOS, Linux, Splunk, Gitlab, Azure DevOps, JIRA, AWS}}      \\
	\descript{Technologies}          & {\location{Docker, Kafka, Kubernetes, TPM, ARM Trustzone, Postgres, Mongo}}     \\
	\descript{Concepts}              & {\location{CI/CD, DevOps, IaC, Microservices, Regression Testing}}                   \\
	\descript{Certifications}		 & {\location{SAFe Program Consultant 4/5, Scrummaster, Scrum@Scale Practitioner}} \\
	\descript{Clearance}			 & {\location{U.S. Top Secret/SCI}} \\
\end{tabular}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Experience
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Work Experience}
\runsubsection{Qualcomm}\descript{| Staff DevOps Engineer}\hfill \location{San Diego, CA | Oct 2022 – Current}
\begin{tightemize}
	\item Reduced virtual machine provisioning time by 90\% via a self-service Terraform Enterprise capability using Nutanix infrastructure.
	\item Improved developer workflow and CI/CD of multiple engineering teams through embedded discovery and enablement of the platform (Jenkins, Docker, Artifactory, Splunk).
	\item Enforced configuration management, role-based access control, and certificate management with Puppet.
\end{tightemize}
\sectionsep
\runsubsection{MITRE}\descript{| Principal Software Delivery Engineer}\hfill \location{San Diego, CA | Apr 2018 – June 2022}
\begin{tightemize}
	\item Led the US Space Force Kobayashi Maru Blue Team (cross-FFRDC) to improve delivery of a large space domain awareness system in response to congressional inquiries (Java, K8s, PostGres).
	\item Reduced development teams lead time to deliver value and improved external collaboration with external partners of MITRE's Aviation Center by building a Kuberenetes-based, internal development platform in AWS Govcloud (Java, EKS, Concourse, SonarQube, Nexus).
    \item Increased deployment frequency (by 5x) of a Navy undersea communications system via software modernization effort that included adopting concepts such as CI/CD, containerization, automated testing, and shifting left on security (Azure DevOps, Docker).
	\item Developed a novel security/privacy architecture and prototype for Dept. of Homeland Security (DHS) to automatically remove permissions from 'risky' mobile applications of enterprise user devices (Python, Firebase, Android).
\end{tightemize}
\sectionsep
\runsubsection{MITRE}\descript{| Software Engineering Manager}\hfill \location{San Diego, CA | August 2015 – June 2022}
\begin{tightemize}
	\item Mentored and coached team members, facilitating skill development, project placement, and career growth.
	\item Conducted performance reviews and made pay/promotion recommendations.
\end{tightemize}
\sectionsep
\runsubsection{MITRE}\descript{| Lead Software Engineer}\hfill \location{Hampton, VA | March 2014 – April 2018}
\begin{tightemize}
	\item Led a multi-team research effort to build a multi-domain command and control architecture via rapid prototyping and experimentation. Has since been transitioned to operational use by the Air Force (Java, Kafka, Microservices, Mongo, Gitlab).
	\item Provided consulting services to the US Army resulting in the creation of a mobile app development capability and app store for training and education.  https://rdl.train.army.mil/catalog/tag/home
\end{tightemize}
\sectionsep
\runsubsection{MITRE}\descript{| Senior Software Engineer}\hfill \location{Hampton, VA | June 2008 – March 2014}
\begin{tightemize}
	\item Created and implemented an enterprise mobile security strategy for the White House Communications Agency that resulted in first agency-wide smartphone deployment.
	\item Operationalized capability with the Special Operations Forces to share unit location information via SMS (no cellular data network) through a custom developed Android app.
	\item Proved the concept of controlling an Army munitions system via smartphone by developing a Windows (Java) and Android app prototype.
\end{tightemize}
\sectionsep
\runsubsection{GDIT}\descript{| Software Engineer}\hfill \location{Suffolk, VA | May 2005 – July 2008}
\begin{tightemize}
	\item Improved the US Joint Forces Command's ability to conduct modelling and simulation exercises by developing a unit order of battle data correlation tool (Java) to automate the creation of simulation initialization data.
\end{tightemize}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Education
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education}
\raggedright

\runsubsection{Old Dominion University}\descript{| MS, BS, Computer Science}\hfill \location{Norfolk, VA}\\
\begin{tightemize}
	\item Master's project presented a novel approach to finding members of an organization online using social media profile friend links (Java, RDF).
\end{tightemize}
\sectionsep
\runsubsection{ODU Web Science Research Group}\descript{| Research Assistant}\hfill \location{Norfolk, VA | May 2009 – May 2011}
\begin{tightemize}
	\item Developed the Firefox Add-On ArchiveFacebook (JavaScript) that provides Facebook users the ability to save and access their data offline (100k+ users).
	\item Created the \href{https://github.com/carltonnorthern/nickname-and-diminutive-names-lookup}{nicknames PyPI package} as a simple way to find variations of first names.
\end{tightemize}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Publications
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Publications}
\raggedright
\begin{tightemize}
	\item \descript{\href{https://scholar.google.com/citations?view_op=view_citation&hl=en&user=83fQz68AAAAJ&citation_for_view=83fQz68AAAAJ:UeHWp8X0CEIC}{Mobile Per-app Security Settings}} - Future of Information and Communications Conference (FICC) 2021
	\item \descript{\href{https://www.dhs.gov/publication/st-evaluating-mobile-app-vetting-integration-enterprise-mobility-management-enterprise}{Evaluating Mobile App Vetting Integration with Enterprise Mobility Management in the Enterprise}} - Department of Homeland Security 2019
	\item \descript{\href{https://mitre.github.io/vulnerable-mobile-apps/}{MITRE Vulnerable and Privacy Violating Mobile Apps}} - Github 2017
	\item \descript{\href{https://scholar.google.com/citations?view_op=view_citation&hl=en&user=83fQz68AAAAJ&citation_for_view=83fQz68AAAAJ:2osOgNQ5qMEC}{Analyzing the effectiveness of app vetting tools in the enterprise}} - \href{https://usmile.at/symposium/2017/program/peck-northern}{Android Security Symposium 2017}
	\item \descript{\href{https://aida.mitre.org/agile/agile-cost-estimation/}{Agile Cost Estimation}} - Acquisition in the Digital Age 2016
	\item \descript{\href{https://trustedcomputinggroup.org/wp-content/uploads/TPM-2-0-Mobile-Reference-Architecture-v2-r142-Specification_FINAL2.pdf}{TPM 2.0 Mobile Specification}} - Trusted Computing Group 2014
	\item \descript{\href{https://scholar.google.com/citations?view_op=view_citation&hl=en&user=83fQz68AAAAJ&citation_for_view=83fQz68AAAAJ:u-x6o8ySG0sC}{An Unsupervised Approach to Discovering and Disambiguating Social Media Profiles}} - Knowledge Discovery and Data Mining (KDD) Conference 2011.
	\item \descript{\href{https://scholar.google.com/citations?view_op=view_citation&hl=en&user=83fQz68AAAAJ&citation_for_view=83fQz68AAAAJ:u5HHmVD_uO8C}{Handbook for implementing agile in department of defense information technology acquisition}} - MITRE Technical Papers 2010
\end{tightemize}
\sectionsep

\
\end{document}
