%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This is a modified ONE COLUMN version of
% the following template:
%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \documentclass[]{deedy-resume-openfont}

    \begin{document}
    
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Profile
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Carlton}{Northern}{carlton.northern@gmail.com | (757) 967-7577 | San Diego, CA | github.com/carltonnorthern}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Skills
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Skills}
\raggedright
\begin{tabular}{ l l }
	\descript{Programming Languages} & {\location{JavaScript, HTML, CSS, PHP, Java, C++, Python, YAML}} \\
	\descript{Platforms}             & {\location{Android, iOS, Linux, Gitlab, Azure DevOps, AWS}}      \\
	\descript{Technologies}          & {\location{Kafka, Docker, Kubernetes, RDF, TPM, ARM Trustzone, Postgres, Mongo}}     \\
	\descript{Concepts}              & {\location{CI/CD, DevOps, IaC, Microservices, regression testing}}                   \\
\end{tabular}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Education
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education}
\raggedright

\runsubsection{Old Dominion University}\descript{| MS, BS, Computer Science}\hfill \location{Norfolk, VA}\\

\sectionsep
\runsubsection{ODU Web Science Research Group}\descript{| Research Assistant}\hfill \location{Norfolk, VA | May 2009 – May 2011}
\begin{tightemize}
	\item Developed the ArchiveFacebook Add-On for Firefox that allows a user of Facebook to archive their content.
\end{tightemize}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Experience
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Work Experience}
\runsubsection{MITRE}\descript{| Principal Software Delivery Engineer}\hfill \location{San Diego, CA | Apr 2018 – Present}
\begin{tightemize}
	\item Leading the Space Force Kobayashi Maru Blue Team (cross-FFRDC) to improve delivery of a large space domain awareness application in response to congressional enagements.   
	\item Coached a Navy NDAA Section 873 Agile - DevOps pilot program. Helped modernize a Navy software development effort by adopting concepts such as CI/CD, containerization, automated testing, and shifting left on security and operational concerns.
\end{tightemize}
\sectionsep
\runsubsection{MITRE}\descript{| Group Leader}\hfill \location{San Diego, CA | August 2015 – Present}
\begin{tightemize}
	\item Care for a team of Software Engineers to ensure they are able to have impact, grow professionally, and have a sense of purpose.
\end{tightemize}
\sectionsep
\runsubsection{MITRE}\descript{| Lead Software Engineer}\hfill \location{Hampton, VA | March 2014 – April 2018}
\begin{tightemize}
	\item Led a multi-team research effort to build a multi-domain command and control architecture via rapid prototyping and experimentation. Has since been transitioned to operational use by the Air Force.
	\item Helped the Army stand up a mobile development capability and app store for training and education.  https://rdl.train.army.mil/catalog/tag/home
\end{tightemize}
\sectionsep
\runsubsection{MITRE}\descript{| Senior Software Engineer}\hfill \location{Hampton, VA | June 2008 – March 2014}
\begin{tightemize}
	\item Developed an Android app to share the location of special forces units using SMS text messages without a data network. 
	\item Developed a Windows and Android app for an Army munitions prototype using Java.
\end{tightemize}
\sectionsep
\runsubsection{GDIT}\descript{| Software Engineer}\hfill \location{Suffolk, VA | May 2005 – July 2008}
\begin{tightemize}
	\item Developed a unit order of battle data correlation tool to aid with modeling and simulation scenario generation data.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Publications
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Publications}
\raggedright

\runsubsection{\large{Mobile Per-app Security Settings}}
- Future of Information and Communications 2021\\
\runsubsection{\large{Assessing and Improving Mobile App Security}}
- Android Security Symposium 2017\\
\runsubsection{\large{TPM 2.0 Mobile Specification}}
- Trusted Computing Group 2014\\
\runsubsection{\large{An Unsupervised Approach to Discovering and Disambiguating Social Media Profiles}}
- Knowledge Discovery and Data Mining Conference 2011\\
\sectionsep

\ 
\end{document}